NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-28 paper/application.tex
update mira update

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the 
To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
summarized  and interpret the attention mechanism.
These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

@@

\subsection{Scenario 3: Assess the Model Prediction Stability}
Utilize input sentence perturbation to assess the overall stability of the prediction

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the 
To better illustrate how the proposed perturbation-driven exploration tool helps the domain experts interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their model analysis workflow.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictStability}
 \caption{
Prediction stability assessment. Isolate unstable one
 }
\label{fig:pipelineView}
\end{figure}

\subsection{Scenario 1: Assess the Model Prediction Stability}
Utilize input sentence perturbation to assess the overall stability of the prediction

\subsection{Scenario 1: Interpreting Decision Making Process}
Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
%
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

@@
